Blog post: Smart quotes, em dashes, and en dashes

### 2020-03-02 text/20/smart-quotes.Rmd
Finished blog entry on smart quotes.

>>>>

Now you might wonder why the internal code for the left double quote (`r x`) does not match the 201C shown above. It turns out that the internal storage of Unicode uses a system called UTF-8. UTF-8 maintains storage efficiency and backwards compatibility with earlier coding systems.

The other smart quote marks are the right double quote,

```{r unicode-3}
cplot("\"\\U201D\"")
```

```{r unicode-4}
cplot("\U201D")
```

```{r unicode-5}
cplot("\"\\U2018\"")
```

```{r unicode-6}
cplot("\U2018")
```

and the right single quote,

```{r unicode-7}
cplot("\"\\U2019\"")
```

```{r unicode-8}
cplot("\U2019")
```

There are a couple of additional codes that I should mention. Most programmers use the minus sign in their coding

```{r minus-1}
cplot("-")
```

but there are two similar characters that you might see. The em dash,

```{r em-dash-1}
cplot("\"\\U2014\"")
```

```{r em-dash-2}
cplot("\U2014")
```

is a longer dash. It has a width equal to the letter "m" in most proportional width fonts. There is another dash, the en dash

```{r en-dash-1}
cplot("\"\\U2013\"")
```

```{r en-dash-2}
cplot("\U2013")
```

that is also longer than a minus sign, but about half the length of the em dash. It has a width that is equal to the letter "n" in most proportional width fonts.

The em dash and en dash will often cause confusion because they look so much like the minus sign, but they will cause problems often in R code.
